\bf Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid

### 2014-09-23 Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid/main.tex
Fixed dash in self-catalysing

This behavior is easiest to understand on the two Trap problems. LTGA's first generation will push individual traps toward a
local optima, but it requires more than a single generation to do so completely. Until that occurs, the model is likely behaving
no better than random as there is little apparent linkage between bits. Once the model begins to identify individual traps crossover
can begin to increase the frequency of higher fitness local optima. This process begins slowly as low fitness local optima are more
likely to be chosen for donation than high fitness local optima due to their frequency in the population. The process becomes self
catalysing as increased frequency of the global optimum trap genes means increased likelihood of the global optimum being spread by crossover.

>>>>

This behavior is easiest to understand on the two Trap problems. LTGA's first generation will push individual traps toward a
local optima, but it requires more than a single generation to do so completely. Until that occurs, the model is likely behaving
no better than random as there is little apparent linkage between bits. Once the model begins to identify individual traps crossover
can begin to increase the frequency of higher fitness local optima. This process begins slowly as low fitness local optima are more
likely to be chosen for donation than high fitness local optima due to their frequency in the population. The process becomes
self-catalysing as increased frequency of the global optimum trap genes means increased likelihood of the global optimum being spread by crossover.
